### 2020-04-21 final_report/results.tex
add section on scaling

\subsection{Supervised Model Evaluation}
\label{sec:modelres}

@@

@@

\subsubsection{Competitive Training}

>>>>

\subsection{Evaluation of Supervised Learning Surrogates}
\label{sec:modelres}

@@

In the next experiment we examine surrogate scaling properties correlating
metrics of interest with progressively increasing training set size. The results
shown in~\cref{fig:scaling} seem to suggest that in terms of regression performance,
methods based on decision trees and neural networks offer the best accuracy on
larger sets overall. This is a curious extension of previous findings, where
gradient boosted trees were observed to significantly dominate over the rest of
the examined methods. With increasing training set size, their relative advantage is
clearly gradually diminished.

@@

According to our experiment, the lowest mean training time is generally achieved
by instance-based learning methods, which seem to offer near-constant scaling
characterists at the expense of significant performance increase later during
prediction. Following that, we observe that the majority of tree-based methods also exhibit
desirable properties. The notable exception here appear to be neural networks,
which are the only model to utilise parallelisation. As such, their constant
synchronisation overhead overall hinders performance on small training sets,
producing misleading results when divided by the number of samples.

In terms of mean prediction time, all tested surrogates except previously mentioned
instance-based learning methods scale exceptionally well. Tree-based generally
models appear to perform the fastest.

\subsubsection{Competitive Surrogate Training}
